Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Truthifying the abstract.
subclauses usually need a subject.

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName, based on
Pottier and Simonet's \origLang.  This
marks the first step towards writing a verified compiler for a language with
information flow types.  Although we did not complete the full noninterference
proof, we were able to find subtle inaccuracies in the \origLang proofs.  
We discuss what would be involved in completing the proof and how this 
relates to other work.

@@

  \begin{case}[$e = \textsf{ if } v \: e_1 \: e_2$ or $e =
    \textsf{ let } x := v \textsf{ in } e$]
    If $e$ is stuck and is an If-statement, then none of \ref{eq:lift-if}, \ref{eq:if-true}, and \ref{eq:if-false} applies. This means that $v$ can neither
    be an integer or some bracketed value.  As a result, $\lift{v}_i$ cannot
    be an integer, and so is stuck.
  \end{case}

>>>>

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName, based on
Pottier and Simonet's \origLang.  This
marks the first step towards writing a verified compiler for a language with
information flow types.  Although we did not complete the full noninterference
proof, we were able to find subtle inaccuracies in \origLang's original
formulation and theorems.  We discuss what would be involved in completing the
proof and how this relates to other work.

@@

  \begin{case}[$e = \textsf{ if } v \: e_1 \: e_2$ or $e =
    \textsf{ let } x := v \textsf{ in } e$]
    If $e$ is stuck and is an If-statement, then none of \ref{eq:lift-if}, \ref{eq:if-true}, and \ref{eq:if-false} applies. This means that $v$ can neither
    be an integer or some bracketed value.  As a result, $\lift{v}_i$ cannot
    be an integer, and so it is stuck.
  \end{case}
